Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-05-22 hpmoon-asoco.tex
Deleting a URL
Minor change in conclusions

Obtained results also show that when the number of islands
\textcolor{blue}{is increased}, the
automatic overlapping method ($A$) significantly improves the results with
respect to the disjoint and overlapped methods. However, this is only
apparent with larger chromosome sizes. Therefore, the length of the
chromosome is also a key factor to take into account in automatic overlapping
methods, and not only the number of islands. 
%Studying this factor with more types of problems, and new configurations of population size and chromosome lengths could be addressed in the future. 
Since our method divides the individuals into blocks of divisible
size, aggregation methods after migration, such as the ones used in
\cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be
also tested. But as complete individuals \textcolor{blue}{are treated} in
each island, the possibility of using a real number, such as 0.3 (30\%
overlapping) instead \textcolor{blue}{of} an integer value opens future experimental
setups. \textcolor{blue}{This should also take care of epistatic
  interactions between chromosome sizes: although variation operators
  operate on chromosome fragments, selection and fitness evaluation
  operates on the whole chromosome; besides, there is migration
  between islands, so the probability of reaching local minima due to
  this fact is, in fact, going to be avoided.}
For example, comparing 
different ways to calculate $c$ using linear, logarithmic or exponential functions
depending on population size, number of islands, or other values, or
using some statistical parameter setting method, such as Taguchi's
\cite{Keratmatpour2018Taguchi}. \textcolor{blue}{However, taking into
  account that the linear change tested in this paper in fact obtains
  good results with a simple formula, it is our conclusion that
  further complication would not be necessary.}

@@

\bibitem{TalbiUnified2018}
E.-G. Talbi,
  \href{https://www.sciencedirect.com/science/article/pii/S074373151830279X}{A
  unified view of parallel multi-objective evolutionary algorithms}, J.
  Parallel Distrib. Comput. (2018) --In press.

>>>>

Obtained results also show that when the number of islands
\textcolor{blue}{is increased}, the
automatic overlapping method ($A$) significantly improves the results with
respect to the disjoint and overlapped methods. However, this is only
apparent with larger chromosome sizes. Therefore, the length of the
chromosome is also a key factor to take into account in automatic overlapping
methods, and not only the number of islands. 
%Studying this factor with more types of problems, and new configurations of population size and chromosome lengths could be addressed in the future. 
Since our method divides the individuals into blocks of divisible
size, aggregation methods after migration, such as the ones used in
\cite{Kimovski15Parallel} or \cite{Dorronsoro13superlinear} can be
also tested. But as complete individuals \textcolor{blue}{are treated} in
each island, the possibility of using a real number, such as 0.3 (30\%
overlapping) instead \textcolor{blue}{of} an integer value opens future experimental
setups. \textcolor{blue}{This should also take care of epistatic
  interactions between chromosome sizes: although variation operators
  operate on chromosome fragments, selection and fitness evaluation
  operates on the whole chromosome; besides, there is migration
  between islands, so the probability of reaching local minima due to
  this fact is, in fact, going to be avoided.}
For example, comparing 
different ways to calculate $c$ using linear, logarithmic or exponential functions
depending on population size, number of islands, or other values, or
using some statistical parameter setting method, such as Taguchi's
\cite{Keratmatpour2018Taguchi}. \textcolor{blue}{However, taking into
  account that the linear change tested in this paper in fact obtains
  good results with a simple formula, it is our conclusion that
  further complication would not be necessary to validate our approach.}

@@

\bibitem{TalbiUnified2018}
E.-G. Talbi,
  A
  unified view of parallel multi-objective evolutionary algorithms, J.
  Parallel Distrib. Comput. (2018) --In press.
